### 2024-05-18 tex/aq_sankey.tex
AQ: grounding line retreat and frontal retreat

  \begin{sankeydiagram}
    % \sankeyset{debug=true}

@@

    \sankeyset{
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/50,
      minimum radius=1mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=1,
        rounded corners=.1em,
        node contents={\name (\qty)},
      },
    }

@@

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        {MELT/Surface melt/\Q{RU}+\Q{RFZ}},
        {ICE-FRET2/ICE and some FRET/\Q{ICE}+0.5*\Q{FRET}},
        {SUB-FRET2/SUB and some FRET/\Q{SUB}+0.5*\Q{FRET}},
        {GROSS/Gross\\accumulation/\Q{DP}+\Q{RFZ}+\Q{SF}+\Q{RF}+\Q{CD}},
        {IL/Ice Loss/
          (\Q{SU}+\Q{RU}+\Q{BM}+\Q{DYN}-(\Q{SF}+\Q{RF}+\Q{CD}+\Q{DP}))},
        {ML/Net mass Loss/\Q{FRET}+\Q{IL}}
      },
    }

@@

    %% GROSS inputs
    \sankeynode{
      name=GROSS,
      quantity=\Q{GROSS}+\Q{IL},
      at={0,0},
      % inputs
      forked={
        \Q{IL}/GROSS-from-IL,  % Ice loss
        \Q{SF}/GROSS-from-SF,   % snowfall
        \Q{DP}/GROSS-from-DP,   % deposition
        \Q{CD}/GROSS-from-CD,   % condensation
        \Q{RF}/GROSS-from-RF,   % rainfall
        \Q{RFZ}/GROSS-from-RFZ  % refrozen melt
      },
    }
    \sankeyadvance{GROSS}{2cm}
    %% GROSS outputs
    \sankeyfork{GROSS}{
      \Q{SU}/GROSS-to-SU,
      \Q{DYN}/GROSS-to-DYN,
      \Q{BM}/GROSS-to-BM,
      \Q{MELT}/GROSS-to-MELT}

    \sankeynode{name=BM, quantity=\Q{BM}, at={[xshift=-3mm, yshift=-3cm]GROSS-to-BM.center}, anchor=center}
    \sankeynode{name=MELT, quantity=\Q{MELT}, at={[xshift=-4mm, yshift=0mm]BM.center}, anchor=left}
    \sankeynode{name=DYN, quantity=\Q{DYN}, at={[xshift=3mm, yshift=0mm]BM.center}, anchor=right}
    \sankeynode{name=DYN-FRET, quantity=\Q{DYN}+\Q{FRET}, at={[xshift=3mm, yshift=-3cm]DYN.center}, anchor=center}

@@

    %% DYN
    \sankeydubins{GROSS-to-DYN}{DYN}
    \sankeyoutin{DYN}{DYN-FRET}
    \sankeynode{name=FRET-DYN, quantity=\Q{FRET}, at={DYN-FRET.center}, anchor=center}
    \sankeyadvance{DYN-FRET}{1cm}
    \sankeyfork{DYN-FRET}{\Q{ICE-FRET2}/ICE-from-DYN, \Q{SUB-FRET2}/SUB}
    \sankeyadvance[ice-to-water]{SUB}{1.5cm}
    \sankeyend[water]{SUB}
    \sankeynode{name=ICE, quantity=\Q{ICE-FRET2}, at={[xshift=3mm, yshift=0mm]SUB.left}, anchor=right}
    \sankeydubins{ICE-from-DYN}{ICE}
    \sankeyend{ICE}

@@

    %% SU
    \sankeynode{name=SU-out, quantity=\Q{SU},
      at={[xshift=10mm, yshift=-10mm]GROSS-to-SU.center}, anchor=center, angle=0}
    \sankeydubins[ice-to-air]{GROSS-to-SU}{SU-out}
    \sankeyend[air]{SU-out}

@@

    \sankeyset{ice}
    \sankeynode{ name=MG, quantity=\Q{FRET}+\Q{IL}, at={[xshift=8mm]SF.left}, anchor=right}
    \sankeystart[red]{MG}
    \sankeyadvance[red-to-ice]{MG}{1cm}
    \sankeyfork{MG}{\Q{FRET}/FRET, \Q{IL}/IL}
    \sankeydubins[minimum radius=2mm]{IL}{GROSS-from-IL}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{30}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{-30}
    \sankeyadvance{FRET}{3cm}
    \sankeydubins{FRET}{FRET-DYN}

@@

    \node[anchor=center, align=center, shift=({0cm,2.25cm})] at (MG.center) {Mass loss (\sankeygetnodeqty{MG}) = \\SMB \& Dynamics (\sankeygetnodeqty{IL})\\+ Frontal retreat (\sankeygetnodeqty{FRET})};

>>>>

  \begin{sankeydiagram}
    %% \sankeyset{debug=true}

@@

    \sankeyset{
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/50,
      minimum radius=1mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        node contents={\name (\qty)},
      },
    }

@@

    \sankeyset{
      def data/.code args={#1/#2/#3}{% node name/label/values
        \LabSet{#1}{#2}
        \QSet{#1}{#3}
        \typeout{#1: \Q{#1} Gt (\Lab{#1})}
      },
      def data/.list={
        %% INSERT_CSV_HERE
        {MELT/Surface melt/\Q{RU}+\Q{RFZ}},
        {ICE-GZRET2/ICE and some GZRET/\Q{ICE}+0.5*\Q{GZRET}},
        {SUB-GZRET2/SUB and some GZRET/\Q{SUB}+0.5*\Q{GZRET}},
        {GROSS/Gross\\accumulation/\Q{DP}+\Q{RFZ}+\Q{SF}+\Q{RF}+\Q{CD}},
        {MG/Mass gain/
          (\Q{SF}+\Q{RF}+\Q{CD}+\Q{DP})-(\Q{SU}+\Q{RU}+\Q{BM}+\Q{DYN})},
        {MGNet/Net mass gain/\Q{MG}-\Q{FRET}-\Q{GZRET}}
      },
    }

@@

    %% GROSS inputs
    \sankeynode{
      name=GROSS,
      quantity=\Q{GROSS}, %+\Q{IL},
      at={0,0},
      % inputs
      forked={
        \Q{SF}/GROSS-from-SF,   % snowfall
        \Q{DP}/GROSS-from-DP,   % deposition
        \Q{CD}/GROSS-from-CD,   % condensation
        \Q{RF}/GROSS-from-RF,   % rainfall
        \Q{RFZ}/GROSS-from-RFZ  % refrozen melt
      },
    }
    \sankeyadvance{GROSS}{2cm}
    %% GROSS outputs
    \sankeyfork{GROSS}{
      \Q{MGNet}/MGNet-from-GROSS,
      \Q{SU}/GROSS-to-SU,
      \Q{FRET}/FRET-from-GROSS,  
      \Q{GZRET}/GZRET-from-GROSS,
      \Q{DYN}/GROSS-to-DYN,
      \Q{BM}/GROSS-to-BM,
      \Q{MELT}/GROSS-to-MELT}

    \sankeynode{name=BM, quantity=\Q{BM}, at={[xshift=-3mm, yshift=-3cm]GROSS-to-BM.center}, anchor=center}
    \sankeynode{name=MELT, quantity=\Q{MELT}, at={[xshift=-4mm, yshift=0mm]BM.center}, anchor=left}
    \sankeynode{name=DYN, quantity=\Q{DYN}, at={[xshift=3mm, yshift=0mm]BM.center}, anchor=right}
    \sankeynode{name=DYN-GZRET, quantity=\Q{DYN}+\Q{GZRET}, at={[xshift=3mm, yshift=-3cm]DYN.center}, anchor=center}

@@

    %% DYN
    \sankeydubins{GROSS-to-DYN}{DYN}
    \sankeyoutin{DYN}{DYN-GZRET}
    \sankeynode{name=GZRET-DYN, quantity=\Q{GZRET}, at={DYN-GZRET.center}, anchor=center}
    \sankeyadvance{DYN-GZRET}{1cm}
    \sankeyfork{DYN-GZRET}{\Q{ICE-GZRET2}/ICE-from-DYN, \Q{SUB-GZRET2}/SUB}
    \sankeyadvance[ice-to-water]{SUB}{1.5cm}
    \sankeyend[water]{SUB}
    \sankeynode{name=ICE, quantity=\Q{ICE-GZRET2}, at={[xshift=3mm, yshift=0mm]SUB.left}, anchor=right}
    \sankeydubins{ICE-from-DYN}{ICE}
    \sankeynode{name=ICE-FRET, quantity=\Q{ICE-GZRET2}+\Q{FRET}, at=ICE.right, anchor=right, forked={\Q{FRET}/FRET, \Q{ICE-GZRET2}/ICE-GZRET3}}
    \sankeyend{ICE-FRET}

    \sankeydubins[minimum radius=1cm]{FRET-from-GROSS}{FRET}

    \sankeyadvance{GZRET-from-GROSS}{1cm}
    \sankeydubins[minimum radius=1cm]{GZRET-from-GROSS}{GZRET-DYN}

@@

    %% SU
    \sankeynode{name=SU-out-tmp, quantity=\Q{SU},
      at={[xshift=5mm, yshift=-35mm]GROSS-to-SU.center}, anchor=center}
    \sankeynode{name=SU-out, quantity=\Q{SU},
      at={[xshift=5mm, yshift=-5mm]SU-out-tmp.center}, anchor=center, angle=0}
    \sankeydubins[ice-to-air]{GROSS-to-SU}{SU-out-tmp}
    \sankeydubins[air,minimum radius=2mm]{SU-out-tmp}{SU-out}
    \sankeyend[air]{SU-out}

    \sankeynode{name=MGNet-out-tmp, quantity=\Q{MGNet},
      at={[xshift=5mm, yshift=-15mm]GROSS-to-SU.center}, anchor=center}
    \sankeynode{name=MGNet-out, quantity=\Q{MGNet},
      at={[xshift=5mm, yshift=-5mm]MGNet-out-tmp.center}, anchor=center, angle=0}
    \sankeydubins[ice]{MGNet-from-GROSS}{MGNet-out-tmp}
    \sankeydubins[ice,minimum radius=2mm]{MGNet-out-tmp}{MGNet-out}
    \sankeyend[ice]{MGNet-out}

@@

    \sankeyset{ice}
    %% \sankeynode{ name=MG, quantity=\Q{MG}, at={[xshift=20mm, yshift=-25mm]GROSS-from-IL.left}, anchor=right, angle=90}
    %% \sankeystart[red]{MG}
    %% %% \sankeyadvance[red-to-ice]{MG}{1cm}
    %% \sankeyfork{MG}{\Q{GZRET}/GZRET, \Q{IL}/IL}
    %% \sankeydubins[minimum radius=0mm]{IL}{GROSS-from-IL}
    %% %% \sankeyadvance{GZRET}{2cm}
    %% %% \sankeyturnleft{GZRET}{30}
    %% %% \sankeyadvance{GZRET}{2cm}
    %% %% \sankeyturnleft{GZRET}{-30}
    %% %% \sankeyadvance{GZRET}{3cm}
    %% \sankeydubins{GZRET}{GZRET-DYN}

@@

    \node[anchor=center, align=center, shift=({0.2cm,1cm})] at (MGNet-out.center) {Net mass gain\\(\sankeygetnodeqty{MGNet-out})};

    \node[anchor=north, align=center, rotate=0, shift=({0cm, 0.0cm})] at (FRET.center) {Frontal retreat \\(\sankeygetnodeqty{FRET})};

    \node[anchor=north, align=center, rotate=0, shift=({0cm, 0.0cm})] at (GZRET-DYN.center) {Grounding line retreat \\(\sankeygetnodeqty{GZRET-DYN})};
